Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-05-17 scripts/MouseSexDiffApril20_2020.Rmd

---
title: "Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Daniel Noble, Alistair
  Senior & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
            toc: true
            code_folding: hide
            toc_depth: 6
            toc_float: yes
            number_sections: yes
            theme: flatly
  html_notebook:
    toc: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

```{r packages, echo = TRUE, eval = FALSE}
library(pacman)
pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here)
```
## Functions 
Functions needed for preparing the data for meta analyses

>>>>

---
title: "Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair
  Senior, Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
            toc: true
            code_folding: hide
            toc_depth: 6
            toc_float: yes
            number_sections: yes
            theme: flatly
  html_notebook:
    toc: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

```{r packages, echo = TRUE, eval = FALSE}
library(pacman)
pacman::p_load(readr, dplyr, metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, pander)
```
## Functions 
Functions needed for preparing the data for meta analyses
